---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

---
title: "cdmb"
output: rmarkdown::pdf_document
vignette: >
  %\VignetteIndexEntry{cdmb}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup}
library(cdmb)
```

# 

General description

Function 1

Function 2

Function 3

Function 4

**`character_counts1()`**

The function character_counts1() takes a character string, splits it into unique characters, counts their occurrences, and returns a bar plot that visualizes these character counts.

\### Example 1: Basic Usage with a Simple Sequence
The example below demonstrates how to use \`character_counts1()\` on a simple string with repeated characters:

```{r}

# Example with a simple repeated character sequence
character_counts1("AABBCCDD")
```

Use cases for the package
