---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

---
title: "cdmb"
output: rmarkdown::pdf_document
vignette: >
  %\VignetteIndexEntry{cdmb}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup}
library(cdmb)
```

# 

# General description

The aim of this R package is to replicate the central dogma of molecular biology

**random_seq ()**

Generates a random DNA sequence of a specified length.

It takes a single argument, len, which determines the length of the sequence to be created.

The function randomly samples from the four DNA nucleotides ("A", "T", "G", "C") with replacement to ensure each position in the sequence is independent of the others.

```{r}
random_seq(7)

```

**dna_to_rna ()**

dna_to_rna takes an input sequence of DNA and transforms it into RNA by substituting the T by U

```{r}
dna_seq <-"ATG"
rna_seq <- dna_to_rna(dna_seq)
print(rna_seq)
```

Function 3

# all_codons function

- The function returns all the codons found in the provided DNA/RNA sequence.
- For function to be executed, user must provide the sequence (RNA or DNA). The `start` argument is an optional offset specifying where in the sequence to start grouping into codons, with a default of 1.
- The output of the sequence is a character vector of the codons found in the provided sequence.
- If the length of the sequence is not a multiple of 3, only the full codons will be returned (the function skips any remaining characters at the end that don’t complete a codon).
- Example usage:
```{r}
all_codons("ATGCGATACAC", start = 1)
```


Function 4

Function 5

Use cases for the package
