---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

---
title: "cdmb"
output: rmarkdown::pdf_document
vignette: >
  %\VignetteIndexEntry{cdmb}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r setup}
library(cdmb)
```

# 

General description

Function 1

Function 2

Function 3

# all_codons function

- The function returns all the codons found in the provided DNA/RNA sequence.
- For function to be executed, user must provide the sequence (RNA or DNA). The `start` argument is an optional offset specifying where in the sequence to start grouping into codons, with a default of 1.
- The output of the sequence is a character vector of the codons found in the provided sequence.
- If the length of the sequence is not a multiple of 3, only the full codons will be returned (the function skips any remaining characters at the end that don’t complete a codon).
- Example usage:
```{r}
all_codons("ATGCGATACAC", start = 1)
```


Function 4

Function 5

Use cases for the package
